### 2014-06-19 ms/ms.Rmd
added a citation

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(c("10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(c("10.3832/ifor0901-006","10.1016/S0378-1127(97)00019-4"))`, `r citep(bib["zianis_biomass_2005"])`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognised need for rich, open data resources to solve ecological problems `r citep(c("10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))`.

>>>>

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(list(bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(c("10.3832/ifor0901-006","10.1016/S0378-1127(97)00019-4"))`, `r citep(bib["zianis_biomass_2005"])`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognised need for rich, open data resources to solve ecological problems `r citep(c("10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))`.
